---
title: "Index"
author: "Mary McCabe"
date: "October 17, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
##Loading librariers
```{r}
library(leaflet)
library(dplyr)
library(tidyr)
library(ggplot2)
library(DT)
```
##Loading the data
```{r}
esc <- read.csv(url("https://knb.ecoinformatics.org/knb/d1/mn/v2/object/urn%3Auuid%3Af119a05b-bbe7-4aea-93c6-85434dcb1c5e", method = "libcurl"), 
                stringsAsFactors = FALSE)
```

```{r}
median_esc <- esc %>% 
  separate(sampleDate, c("Year", "Month", "Day"), sep = "-") %>% 
  group_by(Species, SASAP.Region, Year, Location) %>% 
  summarize(escapement = sum(DailyCount)) %>% 
  group_by(Species) %>% 
  summarize(median_escapement = median(escapement))

head(median_esc)

datatable(median_esc)
```

`coord_flip` switches the axes on the graph
```{r}

ggplot(median_esc, aes(Species, median_escapement)) +
  geom_col() +
  coord_flip()
```

##Maps
### Clean the data
Remove columns that we don't need and keep only one row for each location

```{r}
locations <- esc %>% 
  distinct(Location, Latitude, Longitude) %>% 
  drop_na()

```
#Leaflet
The addTiles() function gets a base layer of tiles from OpenStreetMap which is an open alternative to Google Maps. addMarkers use a bit of an odd syntax in that it looks kind of like ggplot2 code but uses ~ before the column names. This is similar to how the lm function (and others) work but you’ll have to make sure you type the ~ for your map to work.


```{r}

leaflet(locations) %>% 
  addTiles() %>% 
  addMarkers(~ Longitude, ~ Latitude, popup = ~ Location)
```

# Use a custom marker so Leaflet doesn't try to grab the marker images from 
# its CDN (this was brought up in 
# https://github.com/NCEAS/sasap-training/issues/22)

```{r}
markerIcon <- makeIcon(
  iconUrl = "https://cdnjs.cloudflare.com/ajax/libs/leaflet/1.3.1/images/marker-icon.png",
  iconWidth = 25, iconHeight = 41,
  iconAnchorX = 12, iconAnchorY = 41,
  shadowUrl = "https://cdnjs.cloudflare.com/ajax/libs/leaflet/1.3.1/images/marker-shadow.png",
  shadowWidth = 41, shadowHeight = 41,
  shadowAnchorX = 13, shadowAnchorY = 41
)


leaflet(locations) %>% 
  addTiles() %>% 
  addMarkers(~ Longitude, ~ Latitude, popup = ~ Location, icon = markerIcon)

```
